\emph{Light Exposure Behavior Assessment (LEBA)}: Development of a novel instrument to capture light exposure-related behaviours

### 2022-01-08 manuscript.Rmd
Analysis flow chart updated

                    graph [fontname = Helvetica,layout = dot,fontsize = 40, ]

                     node[fontname = Helvetica, shape = rectangle, margin = 0.2, width = 15, height = 1, 
                    fixedsize = true,fontsize = 40]

@@

                    node[fontname = Helvetica, shape = rectangle, margin = 0.2, width = 15, height = 6, 
                    fixedsize = true, fontsize = 40]
                    C[label = 
                    <
                    Factor Identification<br align = 'left'/>
                    Scree Plot: 6 Factors<br align = 'left'/>
                    Parallel Analysis: 6 Factors<br align = 'left'/>
                    Minimum Average Partial Method: 5 Factors<br align = 'left'/>
                    Hull Method: 5 Factors<br align = 'left'/>
                    >
                    ]

                     subgraph cluster_1 {
                      graph[fontname = Helvetica, shape = rectangle]
                      style = rounded
                     node[fontname = Helvetica, margin = 0.2,width = 18, height = 2, 
                    fixedsize = true, fontsize = 38 ]

@@

                    4[label = 'Confirmatory Factor Analysis 
                     on the Five Factor Model (23 Items; N=262)
                      Acceptable Fit ( CFI = .97; TLI= .96; RMSEA = .04, SRMR = .09)']
                     5[label = 'Reliability Analysis on CFA (23 Items; N=262) 
                      Ordinal alpha F1=.93; F2=.83; F3 =.70; F4=.69; F5=.52
                      Mcdonald  omega(total) for the total scale = .73']
                    8[label = 'Measurement Invariance Analysis
                    Residual measurement invariance achieved']
                    9[label = 'Semantic Analysis']
                    10[label = 'LEBA Short Form (18 Items; N=690) 
                      Based on Item Response Theory']
                    }
                subgraph cluster_2 {
                      graph[fontname = Helvetica,shape = rectangle]
                      style = rounded
                     node[fontname = Helvetica, margin = 0.2,width = 18, height = 2, 
                fixedsize = true, fontsize = 38 ]
                    6[label = '6-Factor solution: one factor emerged with only two salient loadings']
                    7[label = 'Rejected']
                    }

@@

}")
library(jpeg)
export_svg(Flowchart1) %>%
  charToRaw() %>%
  rsvg() %>%
  writeJPEG("Manuscript.figures/Flowchart1.jpeg",bg = "white", quality = 1)

>>>>

                    graph [fontname = Helvetica,layout = dot,fontsize = 45, ]

                     node[fontname = Helvetica, shape = rectangle, margin = 0.2, width = 16, height = 2, 
                    fixedsize = true,fontsize = 45]

@@

                    node[fontname = Helvetica, shape = rectangle, margin = 0.2, width = 16, height = 6, 
                    fixedsize = true, fontsize = 45]
                    C[label = 
                    <
                    Factor Identification<br align = 'center'/>
                    Scree Plot: 6 Factors<br align = 'center'/>
                    Parallel Analysis: 6 Factors<br align = 'center'/>
                    Minimum Average Partial Method: 5 Factors<br align = 'center'/>
                    Hull Method: 5 Factors<br align = 'center'/>
                    >
                    ]

                     subgraph cluster_1 {
                      graph[fontname = Helvetica, shape = rectangle]
                      style = rounded
                     node[fontname = Helvetica, margin = 0.2,width = 22, height = 2.5, 
                    fixedsize = true, fontsize = 45]

@@

                    4[label = 'Confirmatory Factor Analysis 
                     on the Five Factor Model (23 Items; N=262)
                      Acceptable Fit ( CFI = .97; TLI= .96; RMSEA = .04, SRMR = .09)']
                     5[label = 'Reliability Analysis on CFA (23 Items; N=262) 
                      Ordinal alpha F1=.93; F2=.83; F3 =.70; F4=.69; F5=.52
                      Mcdonald  omega(total) for the total scale = .73']
                    8[label = 'Measurement Invariance Analysis
                    Residual measurement invariance achieved']
                    9[label = 'Semantic Analysis']
                    10[label = 'LEBA Short Form (18 Items; N=690) 
                      Based on Item Response Theory']
                    }
                subgraph cluster_2 {
                      graph[fontname = Helvetica,shape = rectangle]
                      style = rounded
                     node[fontname = Helvetica, margin = 0.2,width = 18, height = 2.5, 
                fixedsize = true, fontsize = 45 ]
                    6[label = 
                    <
                    6-Factor solution:<br align = 'center'/> 
                    one factor emerged with only two salient loadings
                    >
                    ]
                    7[label = 'Rejected']
                    }

@@

}")

library(jpeg)
export_svg(Flowchart1) %>%
  charToRaw() %>%
  rsvg() %>%
  writeJPEG("Manuscript.figures/Flowchart1.jpeg",bg = "white", quality = 1)
